A Linear Solution of the Linearity Challenge

### 2025-12-24 paper/introduction.tex
github

The rest of the paper is organised as follows.
%
\Cref{sec:calculus} describes the syntax and the operational semantics of \LCP
and states the properties of well-typed processes that we formalise and prove,
namely typing preservation, deadlock freedom and runtime safety.
%
\Cref{sec:agda} presents the Agda formalisation and illustrates its key aspects
with particular emphasis on the representation of channels and of typing
contexts. We assume that the reader is somewhat familiar about Agda, but we also
recall a few key definitions from Agda's standard library.
%
% \Cref{sec:examples} illustrates some examples of \LCP processes as they are
% represented in Agda and shows how to use Agda as an interpreter for \LCP.
%
\Cref{sec:related} discusses related work more in detail by providing a
qualitative and quantitative comparison between the known formalisations of
session/linear calculi.
%
\Cref{sec:conclusion} summarises our contributions and discusses ongoing and
future work.

The formalisation has been carried out using Agda and the source code is
available on GitHub at
\url{https://github.com/boystrange/LinearityChallenge/tree/main/lcp}.

>>>>

The rest of the paper is organised as follows.
%
\Cref{sec:calculus} describes the syntax and the operational semantics of \LCP
and states the properties of well-typed processes that we formalise and prove,
namely typing preservation, deadlock freedom and runtime safety.
%
\Cref{sec:agda} presents the Agda formalisation and illustrates its key aspects
with particular emphasis on the representation of channels and of typing
contexts. We assume that the reader is somewhat familiar about Agda but we
recall the lesser known definitions from Agda's standard library.
%
% \Cref{sec:examples} illustrates some examples of \LCP processes as they are
% represented in Agda and shows how to use Agda as an interpreter for \LCP.
%
\Cref{sec:related} discusses related work more in detail by providing a
qualitative and quantitative comparison between the known formalisations of
session/linear calculi.
%
\Cref{sec:conclusion} summarises our contributions and discusses ongoing and
future work.

The formalisation has been checked with Agda 2.8.0 and the source code is on
GitHub at \url{https://github.com/boystrange/LinearityChallenge/tree/main/lcp}.
